COG-ED Manuscript

### 2022-01-25 06_Paper/COG-ED/Manuscript.Rmd
changed p value for SCA from .01 to .05
updated formatting of JN interval

  sca_results$sign <- ifelse(sca_results$pvalue < .01, sca_results$beta, NA)

@@

Johnson-Neyman intervals:

`r h2c_jn.int`

@@

```{r FigSCA, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Results of the specification curve analysis for the multi level model. The upper panel shows the fixed effect estimates for Need for Cognition and n-back level as predictors of subjective values. Estimates with $p<.01$ are indicated by a dot on the line. The lower panel shows the preprocessing steps of each corresponding pipeline. The $BF10$ of each pipeline's multi level model approached infinity.", fig.pos="H"}

>>>>

  sca_results$sign <- ifelse(sca_results$pvalue < .05, sca_results$beta, NA)

@@

Johnson-Neyman interval:

`r paste("[", round(h2c_jn.int[1], digits = 2), ", ", round(h2c_jn.int[2], digits = 2), "]", sep = "")`

@@

```{r FigSCA, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Results of the specification curve analysis for the multi level model. The upper panel shows the fixed effect estimates for Need for Cognition and n-back level as predictors of subjective values. Estimates with $p<.05$ are indicated by a dot on the line. $N=15$. The lower panel shows the preprocessing steps of each corresponding pipeline. The $BF10$ of each pipeline's multi level model approached infinity.", fig.pos="H"}
